The semantic drift of quotations in blogspace: a case study in short-term cultural evolution

### 2016-05-30 brains-conclusion.tex
chore/todos: rework some todos after rereading Cog. Sci. letter

\todo{\#14: link to introduction discussion, mentioning this can be a model system}

>>>>

\todo{\#14:
link to introduction discussion:
(1) this can be a model system,
(2) convergence can be looked for in any dimension, but that doesn't make a theory, so Epidemiology of Representations is all nice, but:
(3a) taken simplistically it predicts obviously simplistic stuff (all quotes CV. to a single quote),
(3b) taken more realistically (many dimensions in life) it gives some ideas, but it's not clear it's a core principle
(3c) we need more controlled investigation to see how relevant it is.
}
